The title

### 2023-03-28 doc/multiverse.Rmd
Add in time of day relating to most active periods for moderation
Fixes #71

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location")
)
moderator_df$moderator_sentence <- stringr::str_to_sentence(moderator_df$moderator)

@@

```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

>>>>

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location", "pa_mostactivehr"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location", "Pa_mostactivehr")
)
moderator_df$moderator_sentence <- stringr::str_to_sentence(moderator_df$moderator)

@@

```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```
\clearpage

## most active hour

```{r}
tar_load(model_tables_pa_mostactivehr)
```

### The effects of physical activity volume on sleep by most active hour

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by most active hour, and the results are presented in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-volume-fig-by-pa-mostactivehr)

```{r sleep-outcomes-by-pa-mostactivehr}
papaja::apa_table(
  model_tables_pa_mostactivehr$sleep$data,
  caption = model_tables_pa_mostactivehr$sleep$caption,
  note = model_tables_pa_mostactivehr$sleep$note,
  col_spanners = model_tables_pa_mostactivehr$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity volume by most active hour"}
knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Pa_mostactivehr.jpg"), error = FALSE)
```

### The effects of physical activity intensity on sleep by most active hour

We estimated how physical activity intensity affects sleep across most active hour
We present the results in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-intensity-fig-by-pa-mostactivehr).

```{r sleep-by-intensity-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity intensity moderated by most active hour"}
knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Pa_mostactivehr.jpg"), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by most active hour
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-pa-mostactivehr).

```{r pa-outcomes-by-pa-mostactivehr}
papaja::apa_table(
  model_tables_pa_mostactivehr$physical_activity$data,
  caption = model_tables_pa_mostactivehr$physical_activity$caption,
  note = model_tables_pa_mostactivehr$physical_activity$note,
  col_spanners = model_tables_pa_mostactivehr$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep duration moderated by most active hour"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Pa_mostactivehr.jpg"), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by most active hour.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-pa-mostactivehr).

```{r PA-by-sleep-efficiency-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep efficiency moderated by most active hour"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Pa_mostactivehr.jpg"), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by most active hour
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-pa-mostactivehr).

```{r PA-by-sleep-onset-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep onset moderated by most active hour"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Pa_mostactivehr.jpg"), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by most active hour.
Results are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-pa-mostactivehr).

```{r PA-by-sleep-regularity-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep regularity moderated by most active hour"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Pa_mostactivehr.jpg"), error = FALSE)
```
